% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Ian Dunn}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.calpoly.edu/}{California Polytechnic State University} \\
  Computer Science Department \\
  San Luis Obispo, CA 93407
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Fax: &  (919) 962-5678 \\
    Email: & \href{mailto:idunn01@calpoly.edu}{\tt idunn01@calpoly.edu} \\
    Homepage: & \href{http://www.iandunn.me/}{\tt http://www.iandunn.me/} \\
  \end{tabular}
\end{minipage}


\section*{Personal}

\begin{itemize}
\item Born on December 20, 1991.
\item United States Citizen.
\end{itemize}


\section*{Education}

\begin{itemize}
  \item B.S. Software Engineering, California Polytechnic State University, 2016.
  \item M.S. Computer Science, California Polytechnic State Univeristy, 2016.
\end{itemize}


\section*{Employment}

\begin{itemize}
\item {\bf Lecturer}, {\it California Polytechnic State University}. January 2017 - Present. \\
  Instructed courses {\it Game Design}, {\it Systems Programming}, {\it Introduction to Computer Graphics}, {\it Advanced Rendering Techniques}, and {\it Real-Time 3D Computer Graphics Software}.

\item {\bf Software Engineer Intern}, {\it Microsoft}. June - December 2015. \\
  Direct3D 12 team. Created MultiGPU Affinity Layer for Direct3D 12, tool for game engine developers. Presented project results to GAB.

\item {\bf Game Software Engineer Intern}, {\it Intel}. January - May 2015. \\
  Generated C++ source from IntelGPA frame captures. Added Intel hardware metrics to open-source Renderdoc project.

\item {\bf SDET Intern}, {\it Microsoft}. Summer 2014. \\
  Software development, analysis, and research related to social media data and customer sentiment analysis.

\item {\bf Teaching Associate}, {\it California Polytechnic State University}. Fall 2014. \\
  Instructed course {\it System Programming}, managed TA staff. Inverted instruction model.

\item {\bf Research Assistant}, {\it California Polytechnic State University}. Summer 2012, 2013. \\
  Research assistant for Dr. Zoe Wood, graphics professor.
  Worked on volumetric data visualization and surface reconstruction projects.

\end{itemize}


\section*{Publications}

\begin{itemize}
\item Surface Reconstruction of Ancient Water Storage Systems, {\it GRAPP 2014}.
\item Towards Three-Dimensional Underwater Mapping Without Odometry, {\it UUST 2013}.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
  \end{footnotesize}
\end{center}

\end{document}
